Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-10-24 2016-Weak-FH-Bisim/WeakBisim.tex
redaction dans sec 5.4,5.3

\subsection{Composition properties: composition of weak open transitions}
Now the semantics of an open pNet is defined both as an open automaton, and as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pnet that fills its hole.

\subsection{Weak FH-bisimulation}

@@

Weak bisimulation can be alternatively defined as a strong bisimulation on the weak open automata, however this would still need a specific definition of strong bisimulation for weak open automata. \TODO{polish}

\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
reflexive, symmetric and transitive.
\end{theorem}
proof in appendix

@@

\subsection{Weak bisimulation is an equivalence}

@@

\subsection{Composition properties}
This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.

>>>>

\subsection{Composition properties: composition of weak open transitions}
We now have two different semantics for open pNets: a stronf semantics, defined  as an open automaton, and as a weak semantics, defined as a weak open automaton. Like the open automaton, the weak open automaton features valuable composition properties. We can exhibit  a composition property and a decomposition property that relate open pNet composition with their semantics, defined as weak open automata. These are however technically more complex than the ones for open automata because each hole performs a set of actions, and thus a composed transition is the composition of one transition of the top-level pNet and a sequence of transitions of the sub-pNet that fills its hole. They can be found as Lemmas~\ref{lem-decomposeWOT}, Lemma~\ref{lem-Weakcompose1}, and Lemma~\ref{lem-Weakcompose} in~\ref{sec:app-composition}.

\subsection{Weak FH-bisimulation}
For defining a bisimulaiton relation between weak open automatas, two options are possible. Either we define a simulation similar to the strong simulation but based on open automata, this would look like the FH-simulation but would need to be adapted to weak open transitions. Or we define directly and classically a weak FH-simulation as a relation between two open automata, relating the open transition of one open automaton with the transition of the weak open automaton derived from the second one.

The definition below specifies how a set of weak open transitions can simulate an open transition, and under which condition; this is used to relate, by weak FH-bisimulation, two open automata by reasoning on the weak open automata that can be derived from the strong ones.
This is defined formally as follows.

@@

Compared to strong bisimulation, except the obvious use of weak open transitions to simulate an open transition, the condition on predicate is slightly changed concerning actions of the holes. Indeed only the visible actions of the holes must be compared and they form a list of actions, but of length at most one.

Weak FH-bisimilarity is an equivalence in the same way as strong FH-bisimilarity.

\begin{theorem}[Weak FH-Bisimulation is an equivalence]\label{thm-weak-equiv} Suppose $\mathcal{R}$ 
is a weak FH-bisimualtion. Then $\mathcal{R}$ is an equivalence, that is, $\mathcal{R}$ is 
reflexive, symmetric and transitive.
\end{theorem}
The proof  is detailed in \ref{app-WFH-equiv}, it follows a similar pattern as the proof that strong FH-bisimulation is an equivalence, but technical details are different, and in practice we rely on a different (but proven equivalent) definition of weak FH-bisimilarity; this equivalent version simulates a \emph{weak} open transition with a set of weak open transition. The careful use of the best definition of weak FH-bisimilarity makes the proof similar to the strong FH-bisimulation case.

@@

\subsection{Weak bisimulation is an equivalence}\label{app-WFH-equiv}

@@

\subsection{Composition properties}\label{sec:app-composition}
This section gives detailed lemmas and their proofs, these are the equivalent of the composition lemmas for open transitions, but applied to weak automata that give the semantics of open pNets.
